### 2016-01-10 abstract.tex
changes before resubmitting OBS: no commit before minor change in intro

\begin{abstract}
Interatomic Coulombic Decay (ICD) is an electronic decay process after
non-outer-valence ionization. It has been shown to occur in a multitude of small
and large systems.
The effects of more than one possible decay
partner are discussed in detail using NeAr clusters
and pure Ne clusters as examples.
Hereby, the mostly underestimated contribution of decay with
non-nearest neighbours is highlighted. In the neon atoms, the lifetime of the
bulk atoms is found to be in excellent agreement with experiment, while the
lifetimes of the surface atoms differ significantly. Hence, the experimental
lifetime can not purely be explained by the effect of the number of
neighbours.

>>>>

\begin{abstract}
Interatomic Coulombic Decay (ICD) is an electronic decay process of
excited, ionized systems. It has been shown to occur in a multitude of small
and large systems.
The effects of more than one possible decay
partner are discussed in detail illustrated by simulated ICD electron spectra
of NeAr clusters and pure Ne clusters.
Hereby, the mostly underestimated contribution of decay with
non-nearest neighbours is highlighted. In the neon clusters, the lifetime of the
bulk atoms is found to be in excellent agreement with experiment, while the
lifetimes of the surface atoms differ significantly. Hence, the experimental
lifetime can not purely be explained by the effect of the number of
neighbours.

### 2016-01-10 clusters.tex
changes before resubmitting OBS: no commit before minor change in intro

In the neon dimer several vibrational states of the ionized initial state are
involved in the decay. \cite{Santra00_1} It has furthermore been shown, that
the experimentally determined lifetime of $\tau_NeNe=\unit[150\pm 50]{fs}$
\cite{Schnorr13} is only in agreement with those theoretical lifetime
calculations that explicitely include nuclear dynamics of the intermediate state.
\cite{Schnorr15} However, the early lifetime measurements in neon clusters with
a mean cluster size of $<N>=\unit[900]{atoms}$ show a lifetime of
\unit[30]{fs} for surface atoms and \unit[6]{fs} for bulk atoms. This lifetime
decrease is caused by the possibility to decay with several decay partners.
Nuclear dynamics occur in the range of tens of femtoseconds in the dimer.
Additionally, the driving force for a bond contraction after the initial
ionization is higher in dimers than in clusters, where one bond contraction
usually leads to several bond elongations. Therefore, we consider the influence
of nuclear dynamics on the lifetime to be sufficiently small to be able to
neglect them in clusters in a first description.
\cite{Santra01_3,Ohrwall04}
However, in clusters the nuclear
motion might not be fast enough to play a role due to the manifold of
decay partners and the resulting shortening of the lifetime.
In the following, we will focus on the NeNe-ICD part of the
ICD electron spectra of the NeAr clusters and analyze them in more detail.

\begin{figure}[h]
 \centering
 \includegraphics[width=\columnwidth]{pics/rot.pdf}\\
 \includegraphics[width=\columnwidth]{pics/blue.pdf}
 \caption{ICD spectra for the NeNe-ICD part of the structures of set 3 and
          set 5 of the NeAr clusters in Ref. \cite{Fasshauer14_1}
          plotted as stick spectra.
          The different peak groups resemble different pair types
          within the NeAr clusters. The lowest energy peaks (\textbf{(a)})
          refer to nearest neighbours
          of different shells, the peak group \textbf{(b)} refers
          to nearest neighbours within one shell and the peak group \textbf{(c)}
          refers to next nearest neighbours between different shells.
          The other peaks contain both peaks stemming from
          pairs within the same shell as well as pairs consisting of atoms
          of different shells.}
 \label{figure:rot_blue}
\end{figure}

In Figure \ref{figure:rot_blue} the ICD electron spectra for the NeNe-ICD
part of heterogeneous clusters are shown as stick spectra
for set 3 and set 5. Hereby, we stick to the naming and the color code of
Ref. \cite{Fasshauer14_1}. Both spectra exhibit a similar pattern of peak groups.
The groups are found around \unit[1.0]{eV} (group \textbf{(a)}),
around \unit[1.7]{eV} (group \textbf{(b)}), around \unit[2.6]{eV}
(group \textbf{(c)})
and from \unit[3]{eV} to \unit[4]{eV}. By comparing
the interatomic distances of which these peaks originate to their occurance
in the cluster structures, the peak groups can be assigned to atom pairs
within the cluster. For group \textbf{(a)} the peaks stem from decays
between two nearest neighbour atoms of two different shells,
while group \textbf{(b)}
stems from the decay partners being nearest neighbours in the same shell.
Group \textbf{(c)} can be assigned to next-nearest neighbours in adjacent shells
and the other peaks stem from a mixture of pairs which cannot unambigiously
be categorized because different kinds of peaks intersect each other.

@@

Concluding these findings, there is not neccessarily only one kind of nearest
neighbours in clusters. Even the next-nearest neighbours are closer to
twice the interatomic distance of the closest pair with an open decay channel.
Therefore, as formerly supposed, decay partners of twice the closest interatomic
distance indeed have a very small contribution to the total spectrum. However,
all other decay partners do have to be taken into account in order to simulate
an ICD spectrum of clusters.

\subsection{Neon clusters: Icosahedral vs. Cuboctahedral Structure of Clusters}
\label{sec:icofcc}
We study two cluster structures of \unit[55]{atoms} each, where one has an
idealized icosahedral and the other one has an idealized cuboctahedral structure.
They hence consist of 13 core and 42 surface atoms each. It was predicted
theoretically and proven experimentally that the lifetimes of ionized bulk atoms
is shorter than of ionized surface atoms due to the smaller number of direct
neighbours of surface atoms. The experimentally determined lifetimes are
$\tau_{surf} = \unit[30]{fs}$ and $\tau_{bulk} = \unit[6\pm 1]{fs}$.
For our \unit[55]{atom} cluster the decay widths and lifetimes are listed in
Table \ref{table:lifetimes}.

@@

For both the icosahedral and the cuboctahedral cluster structures the lifetimes
of the bulk atoms are in excellent agreement with experiment.
However, the theoretical lifetimes of the surface atoms are significantly
smaller than the experimental lifetime. Let us for a moment assume that the
experimental lifetimes are correct. Then we have to consider three error sources:
the nuclear motion excluded in out approach, the different cluster sizes,
a different stabilization of charges between the
inner-valence ionized and the outer-valence ionized atom compared to the bulk.
In small clusters, the number of face surface atoms is small compared to the
number of edge and vertex atoms in the surface. The larger the clusters are,
the larger is the relative number of the surface atoms. These surface atoms
in face psoitions have more direct neighbours than atoms in vertex positions.
Therefore, our estimated lifetime of the average surface atoms in the small
clusters should be slightly larger than in larger clusters. A pure structure
effect does not explain the difference between the experimental and the
theoretical results.

@@

If the stabilization difference of the inner-valence vacancy between the bulk
and the surface atoms than the corresponding difference of the outer-valence
vacancy, the transferred energy is increased in case of the surface atoms
($\omega_{vp,surf} > \omega_{vp,bulk}$). As a consequence, the decay width
is decreased and the lifetime is increased. Unfortunately, only the initial
state energy differences are to be found in the literature \cite{Ohrwall04}.
Hence, a validation of this cause is currently not possible.

Before discussing the ICD spectra shown in Figure \ref{figure:reinNe} of
the icosahedral and cuboctahedral cluster
structures, we would like to recall that clusters with an icosahedral structure
have shorter interatomic distances between shells than within the same
shell.
In terms of the ICD, different groups of nearest neighbours exist,
one within the same shell and one
between adjacent shells. This is characteristic for icosahedral cluster
structures. Cuboctahedral cluster structures on the other hand are characterized
by only one interatomic distance. 
Therefore, icosahedral cluster structures should be distinguishable from
cuboctahedral clusters by the number of peaks, which can be seen in Figure
\ref{figure:reinNe}.

\begin{figure}[h]
 \centering
 \includegraphics[width=\columnwidth]{pics/reinNe}
 \caption{ICD spectra of pure neon clusters consisting of 55 atoms in
          icosahedral and fcc structure. In clusters with an ideal fcc structure
          all interatomic distances are the same and hence only one peak
          for each shell around any atom in the cluster is to be expected.
          In ideal icosahedral clusters the interatomic distances between atoms
          within the same shell and between atoms in neighbouring atoms
          are different. Therefore two peaks for interactions partners
          at different distances can be expected. This feature might
          help to experimentally identify the underlying structure of clusters.}
 \label{figure:reinNe}
\end{figure}

Two experimental ICD electron spectra of clusters
with a mean cluster size $<N>$ between 47 and 512 atoms
are available in the literature.
\cite{Marburger03,Barth06_2} 
The first experimental spectrum shows a very
broad ICD electron peak without an unambiguously assignable peak structure,
whereas the later results show a main peak of ICD electrons and a smaller peak
at slightly higher kinetic energies (at around \unit[3]{eV})
that was not even assigned to be an ICD peak in the original work. This peak
corresponds to the decay with non-nearest neighbours. However, a further peak
structure is not visible.

Whether or not the cluster structures would be distinguishable in experiment
will depend the vibrational broadening of the peaks, the experimental
resolution and difference of the interatomic distances
and hence the energy difference of the peaks in the spectrum of the
icosahedral structure. In this proof-of-principle discussion
we chose neon clusters for comparison with experiment but for the distinction
of cluster structures it might be recommendable to choose atoms with larger
internuclear distances in clusters.

>>>>

In the neon dimer several vibrational states of the ionized initial state are
involved in the decay. \cite{Santra00_1} It has furthermore been shown, that
the experimentally determined lifetime of $\tau_{NeNe}=\unit[150\pm 50]{fs}$
\cite{Schnorr13} is only in agreement with those theoretical lifetime
calculations that explicitly include nuclear dynamics of the intermediate state.
\cite{Schnorr15} However, the early lifetime measurements in neon clusters with
a mean cluster size of $<N>=\unit[900]{atoms}$ show a lifetime of
\unit[30]{fs} for surface atoms and \unit[6]{fs} for bulk atoms. This lifetime
decrease is caused by the possibility to decay with several decay partners.
Nuclear dynamics occur in the range of tens of femtoseconds in the dimer.
Additionally, the driving force for a bond contraction after the initial
ionization is higher in dimers than in clusters, where one bond contraction
usually leads to several bond elongations. Therefore, we consider the influence
of nuclear dynamics on the lifetime to be sufficiently small to be able to
neglect them in clusters in a first description.
\cite{Santra01_3,Ohrwall04}
However, in clusters the nuclear
motion might not be fast enough to play a role due to the manifold of
decay partners and the resulting shortening of the lifetime.
In the following, we will focus on the NeNe-ICD part of the
ICD electron spectra of the NeAr clusters and analyze them in more detail.

\begin{figure}[h]
 \centering
 \includegraphics[width=0.7\columnwidth]{pics/rot.pdf}\\
 \includegraphics[width=0.7\columnwidth]{pics/blue.pdf}
 \caption{ICD spectra for the NeNe-ICD part of the structures of set 3 and
          set 5 of the NeAr clusters in Ref. \cite{Fasshauer14_1}
          plotted as stick spectra.
          The different peak groups resemble different pair types
          within the NeAr clusters. The lowest energy peaks (\textbf{(a)})
          refer to nearest neighbours
          of different shells, the peak group \textbf{(b)} refers
          to nearest neighbours within one shell and the peak group \textbf{(c)}
          refers to next-nearest neighbours between adjacent shells.
          The other peaks contain both peaks stemming from
          pairs within the same shell as well as pairs consisting of atoms
          of different shells.}
 \label{figure:rot_blue}
\end{figure}

In Figure \ref{figure:rot_blue} the ICD electron spectra for the NeNe-ICD
part of heterogeneous clusters are shown as stick spectra
for set 3 and set 5. Hereby, we stick to the naming and the color code of
Ref. \cite{Fasshauer14_1}. Both spectra exhibit a similar pattern of peak groups.
The groups are found around \unit[1.0]{eV} (group \textbf{(a)}),
around \unit[1.7]{eV} (group \textbf{(b)}), around \unit[2.6]{eV}
(group \textbf{(c)})
and from \unit[3]{eV} to \unit[4]{eV}.
The peak groups can be assigned to atom pairs
within the cluster. For group \textbf{(a)} the peaks stem from decays
between two nearest neighbour atoms of two different shells,
while group \textbf{(b)}
stems from the decay partners being nearest neighbours in the same shell.
Group \textbf{(c)} can be assigned to non-nearest neighbours in adjacent shells
and the other peaks stem from a mixture of pairs which cannot unambigiously
be categorized because different kinds of peaks intersect each other.

@@

Concluding these findings, there is not neccessarily only one kind of nearest
neighbours in clusters. Even the next-nearest neighbours are closer to
twice the interatomic distance of the closest pair with an open decay channel.
Therefore, also non-nearest decay partners need to be taken into account
in order to simulate ICD spectra of clusters.
It can be considered safe to neglect decay partners at sufficiently larger
distances than twice the closest interatomic distance between decay partners
with open channels.

\subsection{Neon clusters: Icosahedral vs. Cuboctahedral Structure of Clusters}
\label{sec:icofcc}
We study two cluster structures of \unit[55]{atoms} each, where one has an
idealized icosahedral and the other one has an idealized cuboctahedral structure.
They hence consist of 13 core and 42 surface atoms each. It was predicted
theoretically and proven experimentally that the lifetimes of ionized bulk atoms
is shorter than of ionized surface atoms due to the smaller number of direct
neighbours of surface atoms. \cite{Santra01_3,Ohrwall04}
The experimentally determined lifetimes are
$\tau_{surf} = \unit[30]{fs}$ and $\tau_{bulk} = \unit[6\pm 1]{fs}$.
For our \unit[55]{atom} cluster the decay widths and lifetimes are listed in
Table \ref{table:lifetimes}.

@@

For both the icosahedral and the cuboctahedral cluster structures the lifetimes
of the bulk atoms are in excellent agreement with experiment.
However, the theoretical lifetimes of the surface atoms are significantly
smaller than the experimental lifetime. Assuming that the
experimental lifetimes are correct, we have to consider three error sources:
1. the nuclear motion excluded in our approach, 2. the different cluster sizes,
and 3. a different stabilization of charges between the
inner-valence ionized and the outer-valence ionized atom compared to the bulk.
In small clusters, the number of face surface atoms is small compared to the
number of edge and vertex atoms in the surface. The larger the clusters are,
the larger is the relative number of the surface atoms. These surface atoms
in face positions have more direct neighbours than atoms in vertex positions.
Therefore, our estimated lifetime of the average surface atoms in the small
clusters should be slightly larger than in larger clusters. A pure structure
effect does not explain the difference between the experimental and the
theoretical results.

@@

If the stabilization difference of the inner-valence vacancy between the bulk
and the surface atoms is larger than the corresponding difference of
the outer-valence
vacancy, the transferred energy is increased in case of the surface atoms
($\omega_{vp,surf} > \omega_{vp,bulk}$). As a consequence, the decay width
is decreased and the lifetime is increased. Unfortunately, only the initial
state energy differences are to be found in the literature \cite{Ohrwall04}.
Hence, a validation of this cause is currently not possible.

Before discussing the ICD spectra  of the icosahedral and cuboctahedral
cluster structures shown in Figure \ref{figure:reinNe}, we would like to
recall that clusters with an icosahedral structure
have shorter interatomic distances between shells than within the same
shell.
In terms of the ICD, different groups of nearest neighbours exist,
one within the same shell and one
between adjacent shells. This is characteristic for icosahedral cluster
structures. Cuboctahedral cluster structures on the other hand are characterized
by only one interatomic distance. 
Therefore, icosahedral cluster structures should be distinguishable from
cuboctahedral clusters by the number of peaks, which can be seen in Figure
\ref{figure:reinNe}.

\begin{figure}[h]
 \centering
 \includegraphics[width=\columnwidth]{pics/reinNe}
 \caption{ICD spectra of pure neon clusters consisting of 55 atoms in
          icosahedral and cuboctahedral structure. In clusters with an
          ideal cuboctahedral structure
          all interatomic distances are the same and hence only one peak
          for each shell around any atom in the cluster is to be expected.
          In ideal icosahedral clusters the interatomic distances between atoms
          within the same shell and between atoms in neighbouring atoms
          are different. Therefore two peaks for interactions partners
          at different distances can be expected. This feature might
          help to experimentally identify the underlying structure of clusters.}
 \label{figure:reinNe}
\end{figure}

Two experimental ICD electron spectra of clusters
with a mean cluster size $<N>$ between 47 and 512 atoms
are available in the literature.
\cite{Marburger03,Barth06_2} 
The first experimental spectrum shows a very
broad ICD electron peak without an unambiguously assignable peak structure,
whereas the later results show a main peak of ICD electrons and a smaller peak
at slightly higher kinetic energies (at around \unit[3]{eV})
that was not even assigned to be an ICD peak in the original work. This peak
corresponds to the decay with non-nearest neighbours in the adjacent shell.
However, a further peak
structure is not visible.

Whether or not the cluster structures would be distinguishable in experiment
will depend on the vibrational broadening of the peaks, the experimental
resolution and difference of the interatomic distances
and hence the energy difference of the peaks in the spectrum of the
icosahedral structure. In this proof-of-principle discussion
we chose neon clusters for comparison with experiment but for the distinction
of cluster structures it might be recommendable to choose atoms with larger
internuclear distances in clusters.

### 2016-01-10 computational.tex
ack, abstract, summary, smaller changes
changes before resubmitting OBS: no commit before minor change in intro

\section{Computational Details}
\label{sec:computational}
The cluster structures used were constructed to have an ideal icosahedral or
face-centered-cubic geometry with optional additional incomplete outermost
shells. These are based on the van der Waals radii for neon
$r_{Ne}=\unit[1.54]{\AA}$
and argon $r_{Ar}=\unit[1.88]{\AA}$ \cite{Bondi64}.
In case of the NeAr clusters two of those
cluster structures from Ref. \cite{Fasshauer14_1} that matched best
with the combination of the argon content in the cluster,
the NeAr-ICD to total
ICD ratio and the peak position of the NeAr-ICD peak were used.
These are $C_{Ar}=3$, $C_{Ne}=1$, $S_{Ne}=7$
for set 3
and $C_{Ar}=2$, $C_{Ne}=1$, $S_{Ne}=13$ for set 5, where $C_{Ar}$ denotes
the edge length of the argon core, $C_{Ne}$ denotes the number of complete
neon shells around the argon core and $S_{Ne}$ denotes the number of 
triangular surfaces additionally covered by neon atoms.

@@

The calculations to obtain the ICD electron spectra of those cluster
structures were performed with
the program HARDRoC \cite{HARDRoC} using experimental ionization energies shown
in Table \ref{table:exp_input} and curves fitted to the decay width of the
NeNe ICD of Ref. \cite{Averbukh06_1}.

>>>>

\section{Computational Details}
\label{sec:computational}
The cluster structures used were constructed to have an ideal icosahedral or
face-centered-cubic geometry with optional additional incomplete outermost
shells. These are based on the van der Waals radii for neon
$r_{Ne}=\unit[1.54]{\AA}$
and argon $r_{Ar}=\unit[1.88]{\AA}$ \cite{Bondi64}.
In case of the NeAr clusters two of those
cluster structures from Ref. \cite{Fasshauer14_1}, where the theoretical
and experimental argon content in the cluster,
the NeAr-ICD to total
ICD ratio and the peak position of the NeAr-ICD peak matched best for a given
manifold (set) of clusters produced under certain experimental conditions,
have been chosen.
These are $C_{Ar}=3$, $C_{Ne}=1$, $S_{Ne}=7$ for set 3
and $C_{Ar}=2$, $C_{Ne}=1$, $S_{Ne}=13$ for set 5 where we used the same
nomenclature as in Ref. \cite{Fasshauer14_1}. Hence, $C_{Ar}$ denotes
the edge length of the argon core, $C_{Ne}$ denotes the number of complete
neon shells around the argon core and $S_{Ne}$ denotes the number of 
triangular surfaces additionally covered by neon atoms.

@@

The calculations to obtain the ICD electron spectra of those cluster
structures were performed with
the program HARDRoC \cite{HARDRoC} using experimental ionization energies shown
in Table \ref{table:exp_input} and curves fitted to the decay width of the
NeNe ICD of Ref. \cite{Averbukh06_1} and the NeAr decay widths of Ref.
\cite{Fasshauer14_1}. These fitted curves yield lifetimes
$\tau=\frac{\hbar}{\Gamma}$ at the corresponding equilibrium distances of
$\tau_{NeNe}= \unit[60]{fs}$ and
$\tau_{NeAr}= \unit[44]{fs}$.

### 2016-01-10 intro.tex
changes before resubmitting OBS: no commit before minor change in intro

The Interatomic Coulombic Decay (ICD) is an electronic decay process of an atom or
molecule (a unit) involving atoms or molecules of the environment. After an
ionization from the sub-valence region of a unit $A$, the vacancy is filled
by an electron of the same unit and the excess energy is transferred to a decay
partner $B$, which subsequently get ionized:

\begin{equation*}
 A^+ + B \rightarrow A^+ + B^+ + e^-_{ICD}  .
\end{equation*}

In the final state,
the two units $A$ and $B$ are both positively charged, repell each other and
thereby undergo a Coulomb explosion. This process was predicted theoretically
\cite{Cederbaum97} and later proven experimentally \cite{Marburger03}. Since then
it has been studied in a multitude of different systems such as small and large
rare gas clusters \cite{many,Fasshauer14_1},
clusters of small molecules \cite{},
quantum dots \cite{Bande13}
and proteins \cite{Harbach13}. Additionally it has given raise to
the investigation of a whole zoo of ICD-like processes (see Ref.
\cite{Hergenhahn11,Jahnke15}
and references therein).

@@

The ICD process was so far mostly discussed for the case of decay partners in
the direct vicinity, because the decay widths with decay partners further away
was considered to be negligible. Therefore, the decay was studied in clusters
up to 13 neon atoms considering the initial ionization of only the central
atom and not the other ones \cite{Santra01_3}. In this study, a higher than
linear dependence of the decay width on the number of neighbours was
observed. A linear dependence would be expected for equally decay partners
at equal distances from the initially ionized atom in the same environment.
Since the decay width in the asymptotic limit shows an 
$1/\omega^{4}_{vp}$-behaviour on the energy of the virtual photon, which
is decreased for a stabilized final state, this additional feature
can be related to
the better energetic stabilization of the doubly ionized
final state in larger clusters \cite{Fasshauer13}.

We showed that decay pathways with decay partners at larger distances need to
be included for larger systems for two reasons:
\begin{enumerate}
 \item In cluster structures more than one pair of units can consist of
       the same atom types and have the same interatomic distance. Hence,
       they are indistinguishable in the spectrum. Since the decay rate
       as well as the peak intensity
       is proportional to the number of such pairs,
       the peaks stemming from several pairs are favoured
       compared to other ones at similar distances. Therefore, peaks
       stemming from decays with distant decay partners can be visible
       in ICD spectra of clusters. \cite{Fasshauer14_1}
 \item The opening of ICD-like decay channels depend on the interatomic
       distance. A channel being closed at the distance to the most direct
       neighbours might be open for interaction partners at slightly
       larger distances. If this particular decay channel is more efficient
       than other decay channels being open for the decay with direct
       neighbours, it can still be visible in the spectrum or even
       outperform the slower decay mechanism and hence they have to be
       taken into account. We have shown this for the case of ICD vs.
       the Electron Transfer Mediated Decay (ETMD3) process in mixed ArXe
       clusters \cite{Fasshauer13,Fasshauer16_1}.
\end{enumerate}
However, this feature of non-nearest neighbour ICD
has so far not been addressed by itself and we will fill the gap in this
paper.

For a test system we choose rare gas clusters are. These are favourable
for the investigation of basic features both
from a theoretical and an experimental point of view. Their spherical
symmetry and their very localized orbitals allow for an comparably easy
theoretical description of the decay processes and the gaseous state
of their components allows for a convenient cleaning of the experimental
setup allowing for higher count rates and therefore a higher resolution
of the spectra. At the same time, the structure of the clusters reveals an
interesting matter of research. Small, ideal clusters exhibit an icosahedral
structure while large clusters have a cuboctahedral structure, which
infinitely extended, yields the solid state face-centered-cubic (fcc) structure.
In the solid state, every single atom is surrounded by twelve other atoms in the
same distance. Surface atoms or even atoms at edges and vertices are rare
compared to the number of atoms in the bulk. 
These atoms being surrounded
However, in small clusters most atoms are surface atoms and are therefore
surrounded by less than the optimal 12 atoms.
In the icosahedral cluster structure the interatomic distance between different
layers are shorter than between atoms of the same layer. 
Therefore,
this structure is favourable in small clusters with a large surface-to-bulk ratio.
Together with the structure change from icosahedral to cuboctahedral
the clusters' properties gradually change towards those of solids and
conductivity as well as magnetizability can be observed. \cite{Benfield92}
It is still unclear at which cluster size the favourable structures changes from
an icosahedral to an cuboctahedral structure. Numbers in the range
of 800--3000 atoms have been reported. \cite{Hartke02,Pahl08}
We propose to use the ICD to be a possible tool to differentiate between
icosahedral and fcc cluster structures using the different distance
patterns in the cluster structures.

We will
therefore first introduce the theoretical concepts in section \ref{sec:theory},
present the computational details in section \ref{sec:computational},
discuss the distance dependency of the ICD in general
in section \ref{sec:partners} and then
zoom in on the NeNe ICD part of the ICD spectra of NeAr clusters
\cite{Fasshauer14_1} in section \ref{sec:near}. Here we will discuss the
peaks and their origin in detail and thereby
raise the question, what a \emph{nearest neighbour} is supposed to be. From
our conclusions we propose the possibility to distinguish cluster structures
of ideal icosahedral and cuboctahedral structures using ICD spectra in
section \ref{sec:icofcc}.

>>>>

The Interatomic Coulombic Decay (ICD) is an electronic decay process of an atom or
molecule (a unit $A$) involving atoms or molecules of the environment. After
creation of a sub-outer-valence vacancy in $A$, this vacancy is filled
by an electron of the same unit and the excess energy (often called the energy of
a virtual photon $\omega_{vp}$) is transferred to a decay
partner $B$, which subsequently gets ionized:

\begin{equation*}
 A^{*+} + B \rightarrow A^+ + B^+ + e^-_{ICD}  .
\end{equation*}

In the final state,
the two units $A$ and $B$ are both positively charged, repell each other and
thereby undergo a Coulomb explosion. This process was predicted theoretically
\cite{Cederbaum97} and later proven experimentally \cite{Marburger03}. Since then
it has been studied in a multitude of different systems such as small and large
rare gas clusters \cite{Santra00_1,Santra01_1,Santra01_3,Ohrwall04,Averbukh06_1,
Lundwall07,Jahnke10,Forstel13,Mucke15,Fasshauer14_1},
clusters of small molecules \cite{Zobeley98,Pernpointner06,Mueller06,
Kryzhevoi11_1,Ghosh13a},
quantum dots \cite{Bande13}, proteins \cite{Harbach13}, it is expected
to play a role in DNA damage in radiation therapy \cite{Alizadeh15}
and may be used to destroy malign
tissue \cite{Gokhberg14,Trinter14}. 
Additionally it has given rise to
the investigation of a manifold of ICD-like processes (see Ref.
\cite{Hergenhahn11,Jahnke15}
and references therein).

@@

The ICD process was so far mostly discussed for the case of decay partners in
the direct vicinity, because the decay widths with decay partners further away
were considered to be negligible. Therefore, the decay was studied in clusters
up to 13 neon atoms of equal interatomic distances considering the initial
ionization of only the central
atom and not the other ones \cite{Santra01_3}. The largest cluster had
a cuboctahedral structure. In this study, a higher than
linear dependence of the decay width on the number of neighbours was
observed. A linear dependence would be expected for equal decay partners
at equal distances from the initially ionized atom in the same environment.
Since the decay width in the asymptotic limit shows an 
$1/\omega^{4}_{vp}$-behaviour on the energy of the virtual photon, which
is decreased for a stabilized final state, this additional feature
can be related to
the better energetic stabilization of the doubly ionized
final state in larger clusters \cite{Fasshauer13}.

It was shown in earlier studies \cite{Fasshauer13,Fasshauer14_1,Fasshauer16_1}
that decay pathways with decay partners at larger distances need to
be included for larger systems for two reasons:
\begin{enumerate}
 \item In cluster structures more than one pair of units can consist of
       the same atom types and have the same interatomic distance. Hence,
       they are indistinguishable in the spectrum. Since the decay rate
       as well as the peak intensity
       is proportional to the number of such pairs,
       the peaks stemming from several pairs are favoured
       compared to other ones at similar distances. Therefore, peaks
       stemming from decays with distant decay partners can be visible
       in ICD spectra of clusters. \cite{Fasshauer14_1}
 \item The opening of ICD-like decay channels depends on the interatomic
       distance, which is characteristic for every atom pair.
       A channel being closed at the distance to the most direct
       neighbours might be open for interaction partners at slightly
       larger distances. If this particular decay channel is more efficient
       than other decay channels being open for the decay with direct
       neighbours, it can still be visible in the spectrum or even
       outperform the slower decay mechanism and hence they have to be
       taken into account. We have shown this for the case of ICD vs.
       the Electron Transfer Mediated Decay (ETMD3) process in mixed ArXe
       clusters \cite{Fasshauer13,Fasshauer16_1}.
\end{enumerate}

Especially in the biological systems, in which ICD is discussed to play an
important role \cite{Alizadeh15,Gokhberg14,Trinter14}
the DNA is surrounded by multiple moving
water molecules which can act as decay partners. Therefore, understanding the
effect of non-nrearest neighbour decay will be crucial to study these systems.
However, this feature of non-nearest neighbour ICD
has so far not been addressed by itself and we will fill the gap in this
paper.

For a test system we choose rare gas clusters. These are favourable
for the investigation of basic features both
from a theoretical and an experimental point of view. Their spherical
symmetry and their very localized orbitals allow for an comparably easy
theoretical description of the decay processes and the gaseous state
of their components allows for a convenient cleaning of the experimental
setup allowing for higher count rates and therefore a higher resolution
of the spectra. At the same time, the structure of the clusters reveals an
interesting matter of research. Small, ideal clusters exhibit an icosahedral
structure while large clusters have a cuboctahedral structure, which
infinitely extended, yields the solid state face-centered-cubic (fcc) structure.
In the solid state, every single atom is surrounded by twelve other atoms in the
same distance. Surface atoms or even atoms at edges and vertices are rare
compared to the number of atoms in the bulk. 
However, in small clusters most atoms are surface atoms and are therefore
surrounded by less than the optimal 12 atoms.
In the icosahedral cluster structure the interatomic distances between different
layers are shorter than between atoms of the same layer. 
Therefore,
this structure is favourable in small clusters with a large surface-to-bulk ratio.
Together with the structure change from icosahedral to cuboctahedral
the clusters' properties gradually change towards those of solids and
conductivity as well as magnetizability can be observed. \cite{Benfield92}
It is still unclear at which cluster size the favourable structure changes from
an icosahedral to an cuboctahedral structure. Numbers in the range
of 800--3000 atoms have been reported. \cite{Hartke02,Pahl08}
We propose to use the ICD to be a possible tool to distinguish between
icosahedral and cuboctahedral cluster structures using the different distance
patterns in the cluster structures.

We will
therefore first introduce the theoretical concepts in section \ref{sec:theory},
present the computational details in section \ref{sec:computational},
discuss the distance dependency of the ICD in general
in section \ref{sec:partners} and then
discuss the NeNe ICD part of the ICD spectra of NeAr clusters
\cite{Fasshauer14_1} in section \ref{sec:near}. Here we will discuss the
peaks and their origin in detail and thereby
raise the question, what a \emph{nearest neighbour} is supposed to be. From
our conclusions we propose the possibility to distinguish cluster structures
of ideal icosahedral and cuboctahedral structures using ICD spectra in
section \ref{sec:icofcc}.

### 2016-01-10 partners.tex
changes before resubmitting OBS: no commit before minor change in intro

\begin{figure}[h]
 \centering
 \includegraphics[width=\columnwidth]{pics/model_RE.pdf}
 \caption{Kinetic energy of the ICD electron depending on the interatomic
          distance of the two atoms involved in the decay within the
          asymptotic approximation. The kinetic energy shows a $1/R$
          behaviour and hence distance changes at small distances lead
          to larger changes in the kinetic energy than at larger distances.}
 \label{figure:model_RE}
\end{figure}
From this diagram it can already be
seen that the kinetic energies stemming from equidistant peaks of
\unit[3]{\AA}, \unit[4]{\AA}, \unit[5]{\AA}, \dots ,\unit[9]{\AA} are
not equidistant in their energy difference but rather decrease for
an increasing interatomic distance.

@@

A similar picture is given by the hypothetical ICD-electron spectrum for
decay partners at distances of \unit[3]{\AA}, \unit[4]{\AA}, \dots,
\unit[9]{\AA} shown in Figure \ref{figure:model_EGamma}. Here, the kinetic
energy of the ICD electron is depicted on the abscissae while the decay
width $\Gamma$ is plotted on the ordinate. Since the decay width is proportional
to the decay rate and hence the decay propability, these spectra can directly
be compared to experimental ICD electron spectra.

>>>>

\begin{figure}[h]
 \centering
 \includegraphics[width=\columnwidth]{pics/model_RE.pdf}
 \caption{Kinetic energy of the ICD electron depending on the interatomic
          distance of the two atoms in an isolated pair
          involved in the decay within the
          asymptotic approximation. The kinetic energy shows a $1/R$
          behaviour and hence distance changes at small distances lead
          to larger changes in the kinetic energy than at larger distances.}
 \label{figure:model_RE}
\end{figure}
From this diagram it can already be
seen that the kinetic energies stemming from equidistant peaks of
\unit[3]{\AA}, \unit[4]{\AA}, \unit[5]{\AA}, \dots , \unit[9]{\AA} are
not equidistant in their energy difference but rather decrease for
an increasing interatomic distance.

@@

A similar picture is given by the hypothetical ICD-electron spectrum for
decay partners at distances of \unit[3]{\AA}, \unit[4]{\AA}, \dots,
\unit[9]{\AA} shown in Figure \ref{figure:model_EGamma}. Here, the kinetic
energy of the ICD electron is depicted on the abscissa while the decay
width $\Gamma$ is plotted on the ordinate. Since the decay width is proportional
to the decay rate and hence the decay probability, these spectra can directly
be compared to experimental ICD electron spectra.
